---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library("tidyverse")

```

```{css}
body {
  font-family: Arial, sans-serif;
  color: #343a40;
  margin: 20px;
  padding: 20px;
}

h1, h2, h3 {
  color: #007bff;
}
}
```

## Advertising relevancy analysis 

### Dataset

The data set was collected by having a user submit a survey form every time they were show ads across the internet and were asked to rank the relevancy to them from 1 - 10.

```{r load_data}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQ9cO8b57Ml11LX05LU67mIwlXUV_kscApDO67cRdG0dDm01byim2WNT-48wOwFXubqqw2P9aTJHQx_/pub?gid=315106395&single=true&output=csv")

latest_data <- logged_data %>% 
  rename(
    timestamp = `Timestamp`,
    ad_source = `Where did you see this ads?`,
    ad_count = `How many ads where you shown in one ad break on youtube, on news article and on your social media feed.`,
    ad_relevance = `From 1 to 10 how much do you feel these ads apply to you?`,
  )
```

### Summary

The average number of ads seen at a time was `r mean(latest_data$ad_count, na.rm = TRUE)`, and the highest reported ad relevance score was `r max(latest_data$ad_relevance, na.rm = TRUE)`.


### Data plots

```{r}
ggplot(latest_data, aes(x = ad_source)) +  
  geom_bar(fill = "blue") +
  labs(title = "Distribution of Ad Sources", x = "Ad Source", y = "Count") +
  theme_minimal()

ggplot(latest_data, aes(x = ad_source, y = ad_relevance)) +  
  geom_bar(stat = "summary", fun = "mean", fill = "purple") +
  labs(title = "Average Ad Relevance by Source", x = "Ad Source", y = "Average Relevance (1-10)") +
  theme_minimal()
```
